Supporting Information : The importance of a complete statistical description of dependence between variables for ecology and related fields

### 2019-04-02 SupportingInformation.Rmd
completed documentations for multiple files

<!--Basic setup-->
```{r setup, echo=F}
knitr::opts_chunk$set(echo = TRUE, fig.pos = "H")
seed<-101
source("mtime.R") #A function needed for caching
library(captioner)
```

@@

<!--Simulation for testing non-parametric statistics with different copulas :
The message=F is to suppress warnings that come when you pass a parameter
of 0 to the Frank or Clayton copulas. These are technicallly boundary cases for these families.
They correspond to the independent copula. The packages we use provide the indepdent copula, but
issue a message.-->
```{r stat_testing_save_and_plot_result, message=F, results="hide", echo=F, cache=T, cache.extra=list(seed,mtime("TestStats_multivar_dataset.R"),mtime("CopulaFunctions.R"),mtime("CopulaFunctions_flexible.R"))}
source("TestStats_multivar_dataset.R")
set.seed(seed)

resultsloc<-"./Results/stat_results/stat_testing/"
spearvals<-seq(from=0,to=0.9,by=0.1)
callfn<-coplist_with_params(spearvals=spearvals)
coplist<-callfn$coplist
ncores<-3
res_pt35_rankF<-mclapply(X=coplist,FUN=worker,numpts=35,numsims=100,rank=F,mc.cores=ncores)
res_pt35_rankT<-mclapply(X=coplist,FUN=worker,numpts=35,numsims=100,rank=T,mc.cores=ncores)
res_pt1000_rankF<-mclapply(X=coplist,FUN=worker,numpts=1000,numsims=100,rank=F,mc.cores=ncores)
res_pt1000_rankT<-mclapply(X=coplist,FUN=worker,numpts=1000,numsims=100,rank=T,mc.cores=ncores)
save(res_pt35_rankF,res_pt35_rankT,res_pt1000_rankF,res_pt1000_rankT,file=paste(resultsloc,"StatTestNumericResults.RData",sep=''))

@@

<!--Simulation for model selection and non-parametric analysis with aphids count data for all 20 sp.-->
```{r modelsel_and_npa_aphid_count_allsp, echo=F, cache=T, cache.extra=list(seed,data_aphid_count,mtime("FittingCopula_selective_loc.R"), mtime("vivj_matrix.R"),mtime("good_loclist.R"),mtime("OurBiCopSelect.R"),mtime("MyBiCopGofTest.R"),mtime("preprocessors.R"),mtime("NonParamStat.R"),mtime("CopulaFunctions.R"), mtime("CopulaFunctions_flexible.R"))}

set.seed(seed)
library(parallel)
source("FittingCopula_selective_loc.R")
RES_all_sp_aphid_count<-mclapply(X=c(1:20),FUN=RES_single_sp,d_allsp=data_aphid_count,
                                 families=c(1,3:10,13,14,16:20),level=0.05,data_pt_thrs=30,
                                 good_loc_given=F,good_loc=NA,mc.cores=3)
saveRDS(RES_all_sp_aphid_count,"./Results/fitting_results/RES_all_sp_aphid_count.RDS")

@@

<!--Simulation for model selection and non-parametric analysis with aphids first flight data for all 20 sp.-->
```{r modelsel_and_npa_aphid_ff_allsp, echo=F, cache=T, cache.extra=list(seed,data_aphid_ff,mtime("FittingCopula_selective_loc.R"), mtime("vivj_matrix.R"),mtime("good_loclist.R"),mtime("OurBiCopSelect.R"),mtime("MyBiCopGofTest.R"),mtime("preprocessors.R"),mtime("NonParamStat.R"),mtime("CopulaFunctions.R"), mtime("CopulaFunctions_flexible.R"))}

set.seed(seed)
library(parallel)
source("FittingCopula_selective_loc.R")
RES_all_sp_aphid_ff<-mclapply(X=c(1:20),FUN=RES_single_sp,d_allsp=data_aphid_ff,
                                 families=c(1,3:10,13,14,16:20),level=0.05,data_pt_thrs=30,
                                 good_loc_given=F,good_loc=NA,mc.cores=3)
saveRDS(RES_all_sp_aphid_ff,"./Results/fitting_results/RES_all_sp_aphid_ff.RDS")

@@

<!--Simulation for model selection and non-parametric analysis with plankton data for all 22 sp.-->
```{r modelsel_and_npa_pns_allsp, echo=F, cache=T, cache.extra=list(seed,data_plankton_north_sea,longs_pns,lats_pns,mtime("FittingCopula_selective_loc.R"), mtime("vivj_matrix.R"),mtime("good_loclist.R"),mtime("OurBiCopSelect.R"),mtime("MyBiCopGofTest.R"),mtime("preprocessors.R"),mtime("NonParamStat.R"),mtime("CopulaFunctions.R"), mtime("CopulaFunctions_flexible.R"))}

set.seed(seed)
library(parallel)
source("FittingCopula_selective_loc.R")
RES_all_sp_pns<-mclapply(X=c(1:22),FUN=RES_single_sp,d_allsp=data_plankton_north_sea,
                              families=c(1,3:10,13,14,16:20),level=0.05,data_pt_thrs=45,
                              good_loc_given=F,good_loc=NA,mc.cores=3)
saveRDS(RES_all_sp_pns,"./Results/fitting_results/RES_all_sp_pns.RDS")

>>>>

<!--Basic setup-->
```{r setup, echo=F}
knitr::opts_chunk$set(echo = TRUE, fig.pos = "H")
seed<-101
source("mtime.R") #A function needed for caching
library(captioner)
library(parallel)
busycores<-detectCores()-2 # for parallell computing with mclapply your computer will use all cores except two.
```

@@

<!--Simulation for testing non-parametric statistics with different copulas :
The message=F is to suppress warnings that come when you pass a parameter
of 0 to the Frank or Clayton copulas. These are technicallly boundary cases for these families.
They correspond to the independent copula. The packages we use provide the indepdent copula, but
issue a message.-->
```{r stat_testing_save_and_plot_result, message=F, results="hide", echo=F, cache=T, cache.extra=list(seed,busycores,mtime("TestStats_multivar_dataset.R"),mtime("CopulaFunctions.R"),mtime("CopulaFunctions_flexible.R"))}
source("TestStats_multivar_dataset.R")
set.seed(seed)

resultsloc<-"./Results/stat_results/stat_testing/"
spearvals<-seq(from=0,to=0.9,by=0.1)
callfn<-coplist_with_params(spearvals=spearvals)
coplist<-callfn$coplist

res_pt35_rankF<-mclapply(X=coplist,FUN=worker,numpts=35,numsims=100,rank=F,mc.cores=busycores)
res_pt35_rankT<-mclapply(X=coplist,FUN=worker,numpts=35,numsims=100,rank=T,mc.cores=busycores)
res_pt1000_rankF<-mclapply(X=coplist,FUN=worker,numpts=1000,numsims=100,rank=F,mc.cores=busycores)
res_pt1000_rankT<-mclapply(X=coplist,FUN=worker,numpts=1000,numsims=100,rank=T,mc.cores=busycores)
save(res_pt35_rankF,res_pt35_rankT,res_pt1000_rankF,res_pt1000_rankT,file=paste(resultsloc,"StatTestNumericResults.RData",sep=''))

@@

<!--Simulation for model selection and non-parametric analysis with aphids count data for all 20 sp.-->
```{r modelsel_and_npa_aphid_count_allsp, echo=F, cache=T, cache.extra=list(seed,busycores,data_aphid_count,mtime("FittingCopula_selective_loc.R"), mtime("vivj_matrix.R"),mtime("good_loclist.R"),mtime("OurBiCopSelect.R"),mtime("MyBiCopGofTest.R"),mtime("preprocessors.R"),mtime("NonParamStat.R"),mtime("CopulaFunctions.R"), mtime("CopulaFunctions_flexible.R"))}

set.seed(seed)
library(parallel)
source("FittingCopula_selective_loc.R")
RES_all_sp_aphid_count<-mclapply(X=c(1:20),FUN=RES_single_sp,d_allsp=data_aphid_count,
                                 families=c(1,3:10,13,14,16:20),level=0.05,data_pt_thrs=30,
                                 good_loc_given=F,good_loc=NA,mc.cores=busycores)
saveRDS(RES_all_sp_aphid_count,"./Results/fitting_results/RES_all_sp_aphid_count.RDS")

@@

<!--Simulation for model selection and non-parametric analysis with aphids first flight data for all 20 sp.-->
```{r modelsel_and_npa_aphid_ff_allsp, echo=F, cache=T, cache.extra=list(seed,busycores,data_aphid_ff,mtime("FittingCopula_selective_loc.R"), mtime("vivj_matrix.R"),mtime("good_loclist.R"),mtime("OurBiCopSelect.R"),mtime("MyBiCopGofTest.R"),mtime("preprocessors.R"),mtime("NonParamStat.R"),mtime("CopulaFunctions.R"), mtime("CopulaFunctions_flexible.R"))}

set.seed(seed)
library(parallel)
source("FittingCopula_selective_loc.R")
RES_all_sp_aphid_ff<-mclapply(X=c(1:20),FUN=RES_single_sp,d_allsp=data_aphid_ff,
                                 families=c(1,3:10,13,14,16:20),level=0.05,data_pt_thrs=30,
                                 good_loc_given=F,good_loc=NA,mc.cores=busycores)
saveRDS(RES_all_sp_aphid_ff,"./Results/fitting_results/RES_all_sp_aphid_ff.RDS")

@@

<!--Simulation for model selection and non-parametric analysis with plankton data for all 22 sp.-->
```{r modelsel_and_npa_pns_allsp, echo=F, cache=T, cache.extra=list(seed,busycores,data_plankton_north_sea,longs_pns,lats_pns,mtime("FittingCopula_selective_loc.R"), mtime("vivj_matrix.R"),mtime("good_loclist.R"),mtime("OurBiCopSelect.R"),mtime("MyBiCopGofTest.R"),mtime("preprocessors.R"),mtime("NonParamStat.R"),mtime("CopulaFunctions.R"), mtime("CopulaFunctions_flexible.R"))}

set.seed(seed)
library(parallel)
source("FittingCopula_selective_loc.R")
RES_all_sp_pns<-mclapply(X=c(1:22),FUN=RES_single_sp,d_allsp=data_plankton_north_sea,
                              families=c(1,3:10,13,14,16:20),level=0.05,data_pt_thrs=45,
                              good_loc_given=F,good_loc=NA,mc.cores=busycores)
saveRDS(RES_all_sp_pns,"./Results/fitting_results/RES_all_sp_pns.RDS")
